
---
title: "Brooklyn College"
author: "Department of Business Management"
date: "Midterm Exam (Fall 2019)"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BUSN 3400 Introduction to Economic and Business Statistics

Please read the questions carefully before you answer the questions. The answers should be written clearly. You are not allowed to use a pencil to write your answers. You can use a calculator when required. **Mobile phones are not allowed.** \



**Question 1 (Descriptive Statistics)**

COMPUTE ALL DESCRIPTIVE STATISTICS – mean, median, mode, quartiles, range, interquartile range, variance, standard deviation, coefficient of variation. (Hint : Do not forget that it is **a SAMPLE** while you calculate variance and standard deviation)

Average wait in minutes for a train; n=15

45, 4, 5, 5, 6, 12, 17, 10, 10, 11, 8, 15, 16, 9, 0 \

**Question 2 (Probability)**

```{r echo = FALSE, message = FALSE, results='asis'}
library(devtools)
a = source_url("https://raw.githubusercontent.com/amanojas/Success-and-Luck/master/Table1.R")
a$value
```


Calculate the following using the **Table 1**. (Drawing a table for joint probabilties will help)

1. P (male) =
2. P (female and smoker) =
3. P (female or smoker) =
4. P (male | smoker) =
5. P (smoker | male) =
6. Is there a relationship between gender and smoking?\

**Question 3 (Binomial Distribution)**

a) A company owns 400 laptops. Each laptop has an 8% probability of notworking.You randomly select 20 laptops for your salespeople.
1. What is the likelihood that 5 will be broken?
2. What is the likelihood that they will all work?
3. What is the likelihood that they will all be broken?\

b) A study indicates that 4% of American teenagers have tattoos. You randomly sample 30 teenagers. What is the likelihood that exactly 3 will have a tattoo?

**Question 4 (Estimation and Inference)**

a) The average grade point average (GPA) of undergraduate students in New York is normally distributed with a population mean of 2.5 and a population standard deviation of 0.5.

1. What is the percentage of students with GPA between 1.3 and 1.8?

2. If a **sample** of 25 students is taken, what is the probability that the sample mean GPA will be between 2.50 and 2.75?\

b) A confidence interval was used to estimate the proportion of new Dell laptop computers that are defective. A random sample of 121 laptops produced the following 95% confidence interval as to the proportion of defectives: 2% ± 0.5% 

1. Is the following statement correct? "We are 95% sure that the true
proportion of new Dell laptops that are defective is 2%." Give an explanation. **(You will get zero points if you do not explain the reasoning behind your answer)**\


**Question 5 (Hypothesis Testing, Z-test)**

a) Suppose a researcher wishes to test Ho: $\mu \le$ 100 milligrams versus H1: $\mu$ > 100 milligrams.She concludes that the population mean is less than 100 milligrams when it is actually 104 milligrams. Is she correct? If not, what "type" of error has she made?

b) The Duracell Battery Company claims that its new Bunnywabbit batteries have a life, on the average, of 1,000 hours. Suppose, you take a sample of 100 batteries and test them. You find:\
$\overline{X}$ = 985 hours
s = 30 hours

State your null and alternative hypotheses clearly. Construct a 95% CIE and decide whether the company’s claim should be rejected or not. 


